Supplement - KDM5C is a sex-biased brake against germline gene expression programs in somatic lineages

### 2024-11-08 submission/supplement.Rmd
fix supplement numbering
fix supplement title

---
title: Supplement - The X-linked intellectual disability gene KDM5C is a sex-biased brake against germline programs in somatic lineages
output: pdf_document
geometry: margin = 1in
font-size: 11pt
header-includes:
   - \renewcommand{\figurename}{Supplementary Figure}
   - \usepackage{caption}
   - \captionsetup[figure]{font=footnotesize, labelfont=bf}
   - \usepackage{sectsty} 
   - \usepackage{helvet}
   - \renewcommand{\familydefault}{\sfdefault}
   - \usepackage{lineno}
   - \linenumbers
   - \renewcommand\linenumberfont{\normalfont\small}
   - \usepackage{setspace}
   - \usepackage{siunitx}
   - \spacing{1.5}
   - \pagenumbering{arabic}
   - \usepackage{indentfirst}

@@

**Supplementary table 3: Germline gene misexpression in _Kdm5c_ mutant EpiLCs.** 1) DESeq2 results table of male _Kdm5c_-KO (_Kdm5c^-/y^_) epiblast-like cells (EpiLCs), with annotations for tissue-enriched genes. 2) Results of Fisher exact test on XY EpiLC tissue-enriched genes. 3) enrichPlot gene ontology results of germline-enriched genes misexpressed in male _Kdm5c_-KO EpiLCs, amygdala, and hippocampus. 4) DESeq2 results table of XX _Kdm5c_-HET (_Kdm5c^-/+^_) EpiLCs 5) DESeq2 results table of XX _Kdm5c_-KO (_Kdm5c^-/-^_) EpiLCs 6) Germline genes misexpressed in XY _Kdm5c_-KO, XX _Kdm5c_-KO, and XX _Kdm5c_-HET EpiLCs. 5) enrichPlot gene ontology results of germline genes misexpressed in male versus female _Kdm5c_ mutant EpiLCs

>>>>

---
title: Supplement - KDM5C is a sex-biased brake against germline gene expression programs in somatic lineages
output: pdf_document
geometry: margin = 1in
font-size: 11pt
header-includes:
   - \renewcommand{\figurename}{Supplementary Figure}
   - \usepackage{caption}
   - \captionsetup[figure]{font=footnotesize, labelfont=bf}
   - \usepackage{sectsty} 
   - \usepackage{helvet}
   - \renewcommand{\familydefault}{\sfdefault}
   - \usepackage{lineno}
   - \linenumbers
   - \renewcommand\linenumberfont{\normalfont\small}
   - \usepackage{setspace}
   - \usepackage{siunitx}
   - \spacing{1.5}
   - \pagenumbering{arabic}
   - \usepackage{indentfirst}

@@

**Supplementary table 3: Germline gene misexpression in _Kdm5c_ mutant EpiLCs.** 1) DESeq2 results table of male _Kdm5c_-KO (_Kdm5c^-/y^_) epiblast-like cells (EpiLCs), with annotations for tissue-enriched genes. 2) Results of Fisher exact test on XY EpiLC tissue-enriched genes. 3) enrichPlot gene ontology results of germline-enriched genes misexpressed in male _Kdm5c_-KO EpiLCs, amygdala, and hippocampus. 4) DESeq2 results table of XX _Kdm5c_-HET (_Kdm5c^-/+^_) EpiLCs 5) DESeq2 results table of XX _Kdm5c_-KO (_Kdm5c^-/-^_) EpiLCs 6) Germline genes misexpressed in XY _Kdm5c_-KO, XX _Kdm5c_-KO, and XX _Kdm5c_-HET EpiLCs. 7) enrichPlot gene ontology results of germline genes misexpressed in male versus female _Kdm5c_ mutant EpiLCs
